\section{Out of the box Modules}
 Spring XD provides wide range of Streaming and batch Batch job modules out of the box which implement 
some of the most commonly used streaming and batch job workflows. All the modules can readily be configured and deployed.
Spring XD also supports developing a custom module for any usecase driven functionality.

\subsection{Source modules}

  Source modules ingest data from outside into Spring XD which include, file, gemfire,
http, jdbc, jms, kafka, mail, mqtt, rabbit, reactor-ip, reactor-syslog, sftp, 
syslog (tcp/udp), 
tail, tcp-client, tcp, twittersearch, twitterstream.

\subsection{Processor Modules}
  Processor modules get the data out of source module or the previous processor module, transforms
the data and make the data available for the subsequent processor module or a sink module.
These include aggregator, analytic-pmml, bridge, filter, http-client, json-to-tuple,
object-to-json, script, shell command processor, splitter, transform.

\subsection{Sink Modules}
  Sink modules write the data into the final destination in the streaming application.
These include file, gemfire, hdfs with dataset, hdfs, jdbc, kafka, log, mail, mongodb,
mqtt, rabbit, redis, router, shell command processor, splunk, tcp and metrics modules.

\subsection{Job Modules}

  Job modules provide complete support to run batch jobs that adhere to JSR standardization of
batch processing JSR-352. By deploying these modules into Spring XD, one can avail the 
features like partitioning, job execution orchestration, monitoring and  management
automatically. 

\par

The use cases that out of the box job modules address are poll a directory and import CSV files to HDFS, 
import CSV files to JDBC, HDFS to JDBC export, JDBC to HDFS import, HFDS to mongodb export, copy files from FTP to HDFS, 
run a Spark application (Spark MLLib, Streaming etc.,) as a batch job and 
run a Sqoop application as a batch job

